Manifold Destiny - or how to rig an election

### 2023-12-27 presentation.qmd
abc
befrev

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

>>>>

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---
